---
title: "pinellas-eviciton-scraper-run"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

### Load Libraries

```{r results='hide', message=FALSE}
library(tidyverse) # Tidy functions
library(RSelenium) # Headless browser
library(XML) # For extracting info from HTML
library(seleniumPipes) # For additional Selenium features
library(rvest) # For extracting info from HTML
library(RCurl) # For extracting URL
library(janitor) # For cleaning up scraped data
library(reticulate) # For injecting Python
```

### Include scraper functions

```{r}
source("pinellas-eviction-scraper-functions.R")
```

### Set up headless browser

```{r results='hide', message=FALSE}
## Activate Headless Driver
# Create and initialize driver
rD1 <- rsDriver(browser = c("chrome"),
                port = 4960L,
                # To find Chrome ver. num., use binman::list_versions("chromedriver"); try multiple
                chromever = "83.0.4103.39")

# rD2 <- rsDriver(browser = c("firefox"))

remote_driver <- rD1[["client"]]
# remote_driver <- rD2[["client"]]

```

### Store date ranges to scrape

```{r}
# Store series of date ranges in one-month intervals 
dates_ls <- list(
                 # list("06/01/2020", "06/30/2020"), # 2020
                 # list("05/01/2020", "05/31/2020"),
                 # list("04/01/2020", "04/30/2020"),
                 # list("03/01/2020", "03/31/2020"),
                 # list("02/01/2020", "02/29/2020"),
                 # list("01/01/2020", "01/31/2020"),
                 # list("12/01/2019", "12/31/2019"), # 2019
                 # list("11/01/2019", "11/30/2019"),
                 list("10/01/2019", "10/31/2019"),
                 list("09/01/2019", "09/30/2019"),
                 list("08/01/2019", "08/31/2019"),
                 list("07/01/2019", "07/31/2019"),
                 list("06/01/2019", "06/30/2019"),
                 list("05/01/2019", "05/31/2019"),
                 list("04/01/2019", "04/30/2019"),
                 list("03/01/2019", "03/31/2019"),
                 list("02/01/2019", "02/28/2019"),
                 list("01/01/2019", "01/31/2019")
                 )
```

## Scraper deployment

### Navigate to website & log in

```{r}
navigate_to_pinellas_courts_home()
login_to_pinellas_courts()
enter_all_case_search()
```

### Scrape only the basic case info over a given date range

```{r}
# Set counter to store position in case of crash or timeout
dates_ls_pos = 1

# Run the scraper
for(i in dates_ls_pos:length(dates_ls)) {
  # Get month-year for filename
  dates_filename <- as.character(dates_ls[[dates_ls_pos]][1]) %>%
      str_replace_all('(/\\d\\d/)', '-')
  # enter a range of dates
  enter_date_range(dates_ls_pos)
  # store the basic data
  cases_df_clean <- store_basic_info(dates_ls_pos)
  # write the basic data to a file
  write.csv(cases_df_clean, paste0('data/by-month/basic-info/eviction_cases_', dates_filename, '.csv'))
  # return to the search page
  return_to_search()
  # increment the counter
  dates_ls_pos <- dates_ls_pos + 1
}

# Reset the counter
dates_ls_pos = 1

```

### Scrape details of each case over a given date range

```{r}
# Run the details scraper

sink(file = "data/log.txt", type = "output") # Debugging

# Set counter to store position in case of crash or timeout
dates_ls_pos = 1

# Iterate over all date ranges
for(i in dates_ls_pos:length(dates_ls)) {
  enter_date_range(dates_ls_pos)
  # Set (or reset) the counter for case_num
  case_num_pos = 1
  
  #### DATA PREPARATION ####
  # Set a monthly FINANCIAL data frame
  fin_data<- data.frame(case_number= as.character(), 
                          to_pay = as.character(), 
                          paid = as.character(), 
                          balance = as.character())
  
  # Set a monthly ADDRESS data frame
  address_data<- data.frame(case_number = as.character(),
                            def_address = as.character(),
                            plaint_address = as.character())
  
  # Count cases on page
  num_cases <- how_many_cases()
  
  # Get month / year for filename
  dates_filename <- as.character(dates_ls[[dates_ls_pos]][1]) %>%
      str_replace_all('(/\\d\\d/)', '-')
  
  ##### DATA COLLECTION: BASIC CASE INFO ####
  cases_df_clean <- store_basic_info(dates_ls_pos)
  write.csv(cases_df_clean, paste0('data/by-month/basic-info/eviction_cases_', dates_filename, '.csv'))
  
  # Iterate over all cases within the date range
  for(j in case_num_pos:num_cases) {
  # for(j in case_num_pos:4) { # FLAG this is in testing mode
    view_case(case_num_pos, dates_ls_pos)
    Sys.sleep(1)
    
    #### DATA COLLECTION: CASE DETAILS ####
    # Collect FINANCIAL data
    fin_data <- bind_rows(fin_data, get_financials(dates_ls_pos, case_num_pos))
    print(paste0('Financial data retrieved from ', fin_data$case_number[case_num_pos], ' in month ', dates_filename))
    
    # Collect ADDRESS data
    address_data <- bind_rows(address_data, get_addresses(dates_ls_pos, case_num_pos))
    print(paste0('Address data retrieved from ', address_data$case_number[case_num_pos], ' in month ', dates_filename))
    
    # Increment the position in the case list
    case_num_pos <- case_num_pos + 1
    return_to_results(dates_ls_pos)
  }
  
  #### DATA STORAGE ####
  # Set a counter for the save file name
  if (dates_ls_pos < 10){
    dates_ls_pos_ch <- paste0("00", as.character(dates_ls_pos))
  } else if (case_num_pos < 100) {
    dates_ls_pos_ch <- paste0("0", as.character(dates_ls_pos))
  } else {
    dates_ls_pos_ch <- as.character(dates_ls_pos)
  }
  
  # Store FINANCIALS data
  write.csv(fin_data, paste0('data/by-month/financials/eviction_cases_', dates_filename, '.csv'))
  
  # Store ADDRESS data
  write.csv(address_data, paste0('data/by-month/addresses/eviction_cases_', dates_filename, '.csv'))
  
  # Increment the dates position counter
  dates_ls_pos <- dates_ls_pos + 1
  return_to_search()
}

# Reset the date counter
dates_ls_pos = 1

# Turn off sink
sink.reset()
```

## Work with downloaded info

### Clean up and combine CSVs into a single file

#### Basic info cleaning and combining

```{r results='hide', message=FALSE}

# Read in all CSVs
all_cases_basic <- list.files("data/by-month/basic-info", 
           "*.csv",
           full.names=TRUE) %>%
  map_dfr(read_csv) %>%
  select(-'X1')

# Clean up the combined dataframe
all_cases_basic_clean <- all_cases_basic %>% 
  # Drop empty columns
  select(-`Citation Number`, -`Charge(s)`) %>%
  # Break out date/location/officer
  mutate(Date_Filed = str_sub(`Filed/Location/Judicial Officer`,1,10),
         Location = str_sub(`Filed/Location/Judicial Officer`,11,20),
         Judicial_Officer = str_sub(`Filed/Location/Judicial Officer`,21)
  ) %>%
  select(-`Filed/Location/Judicial Officer`) %>%
  # Make everything lowercase
  mutate_all(~tolower(.)) %>%
  rename_all(~tolower(.)) %>%
  # Split out plaintif / defendants
  separate(col = `style/defendant info`,
           into = c("plaintiff", "defendant"),
           sep = "vs\\."
  ) %>%
  # Strip newlines and carriage returns
  mutate_all(~str_replace_all(., "[\r\n]" , "")) %>%
  # Clean up col names
  rename_all(tolower) %>%
  clean_names() %>%
  mutate_all(~trimws(., "both"))


```

#### Store the combined basic data
```{r}
write.csv(all_cases_basic_clean, "data/eviction_cases_basic_jan2019_june2020.csv")
```

#### Detailed info cleaning and combining

```{r results='hide', message=FALSE}

# Read in all CSVs

## Financials
all_cases_fin <- list.files("data/by-month/financials", 
           "*.csv",
           full.names=TRUE) %>%
  map_dfr(read_csv) %>%
  select(-'X1') %>%
  mutate_all(~trimws(., "both"))

## Addresses
all_cases_addresses <- list.files("data/by-month/addresses", 
           "*.csv",
           full.names=TRUE) %>%
  map_dfr(read_csv) %>%
  select(-'X1') %>%
  mutate_all(~trimws(., "both"))


```

#### Store the combined detailed data in separate csvs
```{r}
write.csv(all_cases_fin, "data/eviction_cases_financials_january2019_june2020.csv")
write.csv(all_cases_addresses, "data/eviction_cases_addresses_january2019_june2020.csv")

  
```

#### Join cleaned + combined basic and detailed info into one data frame

```{r}

all_cases_detailed <- all_cases_basic_clean %>%
  left_join(all_cases_fin) %>%
  left_join(all_cases_addresses)

write.csv(all_cases_detailed, "data/eviction_cases_all_feb2020_june2020.csv")

```



### Sanity checks 

```{r}
# sanity checks
fin_data %>% 
  group_by(case_number) %>% 
  filter(case_number == "")
  count() %>% 
  filter(n>1) %>% 
  nrow()

t <- read_csv("data/eviction_cases_financials_DATERANGE.csv")
t %>% group_by(case_number) %>%
  count() %>%
  filter(n>1) %>%
  nrow()

t <- read_csv("data/eviction_cases_financials_DATERANGE.csv") %>%
  select(-"X1") %>%
  full_join(read_csv("data/eviction_cases_addresses_DATERANGE.csv"), by= c("case_number" = "case_num")) %>%
  select(-"X1")
t %>% filter(is.na(def_address))

# Drop duplicate case numbers or figure out why they get generated during the failsafe reloop.

```
### View details about a single case
```{r}
# Enter a date range
enter_date_range(1)
view_case(1,1)
```

## Cleanup

```{r}
# Stop the server
rD1$server$stop()

```
